### 2015-02-18 paper_40_mpi.tex
minor updates to the satisfaction formula, broke it into 2 formulas

                Mathematically, the following is an algorithm to calculate the 
                satisfaction element score
                of MPI.
                \[
                    S_2 = \frac{\sum^n_{i=1}\left( \frac{\sum^m_{j=1}a_{ij}- \frac{min + max}{2}}{m}  \right)}{n}
                \]

                \begin{itemize}
                    \item $a_{i j}$ answer to question $j$ for app $i$
                    \item $m$ number of questions with equal weights
                    \item $n$ number of apps
                    \item $min$ minimum score for a question
                    \item $max$ maximum score for a question
                \end{itemize}

@@

            The score is based upon the historical deviance of estimates for
            projects.  The top score of
            100 will be obtained when the schedule is met exactly.  A historical average 
            of deviance of schedule will be used to determine an appropriate range
            of schedule adherence.  A schedule that occurs within that range will be awarded
            a score of 0 or above, with less deviance being awarded more points.  Schedules
            that do not fall within the range of deviance will be awarded negative scores, 
            with a greater deviance resulting in a lower score all the way to -100 which means
            the package took twice as long as expected or more.
            For example, a package that takes more than twice as long to deliver than
            estimated will receive a score of -100.

>>>>

                First the score for each question needs to be calculated.

                \[
                    S_{3_i} = \sum^n_{i=1}\left( k \times \frac{ \sum^m_{j=1}a_{ij}-\frac{min + max}{2}}{m} \right)
                \]

                \begin{itemize}
                    \item $a_{ij}$ answer to question $i$ for respondent $j$
                    \item $n$ number of questions
                    \item $m$ number of respondents
                    \item $min$ minimum score for a question
                    \item $max$ maximum score for a question
                \end{itemize}

                Then the satisfaction score is calculated as below.  Use a weighted average
                to combine the question scores.

                \[
                    S_{3} = \sum\limits^n_{i=1} w'_i S_{3_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]

@@
